Title Goes Here

### 2017-08-17 analysis/paper/paper.Rmd
email survey analysis basically complete

We conducted a pilot study to explore data sharing in archaeology. Our sample focused on _Journal of Archaeological Science_ articles on experiments with stone artefacts that were published during `r min(email_survey$'publication year', na.rm = TRUE)` and `r max(email_survey$'publication year', na.rm = TRUE)`. We focused on stone artefact experiments because the all research materials are generated by the researcher so there are not other stakeholders to consider when determining how to share the data: the researcher has complete control over the data. There are also no risks of damage to people or property in sharing these data because they do not include archaeological sites or human subjects. In contacting the authors, we requested the datasets for use in a graduate seminar with the aim of reproducing the published results and further exploring the data (this stage is still in progress). We promised to contact the authors if we discovered anything new, and not to share the data further without their permission.

We sent out `r emails_out` emails to authors of these papers, and received `r emails_back`, resulting in a `r email_response_rate`% response rate. We recieved `r data_items_received` responses that included data files, giving an overall sharing rate of `r sharing_rate`%. Wi

change over time...

location...
student or not...

>>>>

We conducted a pilot study to explore data sharing in archaeology. Our sample focused on _Journal of Archaeological Science_ articles on experiments with stone artefacts that were published during `r min(email_survey$'publication year', na.rm = TRUE)` and `r max(email_survey$'publication year', na.rm = TRUE)`. We focused on stone artefact experiments because the all research materials are generated by the researcher so there are not other stakeholders to consider when determining how to share the data: the researcher has complete control over the data. There are also no risks of damage to people or property in sharing these data because they do not include archaeological sites or human subjects. In contacting the authors, we requested the datasets for use in a graduate seminar with the aim of reproducing the published results and further exploring the data (this stage is still in progress). We promised to contact the authors if we discovered anything new, and not to share the data further without their permission. The data included with this paper is anonymised so the specific authors we contacted cannot be identified.

We sent out `r emails_out` emails to authors of these papers, and received `r emails_back`, resulting in a `r email_response_rate`% response rate. We recieved `r data_items_received` responses that included data files, giving an overall sharing rate of `r sharing_rate`%. We found no clear relationship of data sharing and date of publication. We do not have any insights into why authors of older papers decline to share, but three of the six responses for papers published in 2014-2015 said they declined to share data because they intend to use these data in a future publication. Other noteworthy reasons for delining to share include the author about to defend their thesis or about to go on vacation. We interpret these to mean that the author does not have time to prepare their data for sharing, perhaps because the data are not already well-organised. We found no effect on the author's student status at time of publication on data sharing behaviours, with roughly equal proportions of students and non-students sharing and not sharing.

```{r date-and-sharing, fig.cap="There is no obvious trend in data sharing becavious and date of publication"}
library(viridis)
years <- seq(min(email_survey$'publication year', na.rm = TRUE),
    max(email_survey$'publication year', na.rm = TRUE), 1)
email_survey %>% 
  filter(!is.na( `email sent date`)) %>% 
  group_by(`publication year`, `content recieved date`) %>% 
  tally() %>% 
  filter(!is.na(`publication year`)) %>% 
  mutate(`content recieved date` = if_else(!is.na(`content recieved date`), 
  "yes", "no")) %>% 
  ggplot(aes(`publication year`, n)) +
    geom_col(aes(fill = `content recieved date`),
             position = position_dodge(preserve = 'single')) +
    scale_fill_viridis(discrete = TRUE,
                       guide = guide_legend(title = "Data shared?")) +
    scale_x_continuous(breaks = years,
                       labels = years) +
    theme_bw()

```{r student, fig.cap="No relationship between student status and data sharing behaviour"}
email_survey %>% 
  filter(!is.na( `email sent date`)) %>% 
    mutate(`content recieved date` = if_else(!is.na(`content recieved date`), 
  "yes", "no")) %>% 
  group_by(
  `author is graduate student at time of publication?`, 
  `content recieved date`) %>% 
  tally() %>% 
  filter(!is.na(`author is graduate student at time of publication?`)) %>% 
  ggplot(aes(`author is graduate student at time of publication?`, n)) +
    geom_col(aes(fill = `content recieved date`),
             position = position_dodge(preserve = 'single')) +
    scale_fill_viridis(discrete = TRUE,
                       guide = guide_legend(title = "Data shared?")) +
    theme_bw()
```

```{r}
email_survey %>% 
  filter(!is.na( `email sent date`)) %>% 
    mutate(`content recieved date` = if_else(!is.na(`content recieved date`), 
  "yes", "no")) %>% 
  group_by(
  `author home`, 
  `content recieved date`) %>% 
  tally() %>% 
  filter(!is.na(`author home`)) %>% 
  ggplot(aes(`author home`, n)) +
    geom_col(aes(fill = `content recieved date`),
             position = position_dodge(preserve = 'single')) +
    scale_fill_viridis(discrete = TRUE,
                       guide = guide_legend(title = "Data shared?")) +
    theme_bw()
```

```{r}
email_survey %>% 
  filter(!is.na( `email sent date`)) %>% 
    mutate(`content recieved date` = if_else(!is.na(`content recieved date`), 
  "yes", "no")) %>% 
  group_by(
  journal, 
  `content recieved date`) %>% 
  tally() %>% 
  filter(!is.na(journal)) %>% 
  ggplot(aes(journal, n)) +
    geom_col(aes(fill = `content recieved date`),
             position = position_dodge(preserve = 'single')) +
    scale_fill_viridis(discrete = TRUE,
                       guide = guide_legend(title = "Data shared?")) +
    theme_bw()
```
